PRISM protocol v0.3

### 2021-10-05 prism-backend/research/article.tex
Updated ECIES and Connector models to meet more closely standard ECIES.

@@

@@

Notes:
\begin{itemize}
\item we could change the $CreateDID$ event to incorporate an optional batcher DID from start, the batcher DID would be part of the initial state, 
      bounding the batcher to the DID suffix. 
\item we could support events to de-register from a batcher, and to switch batcher too.
\item a user is free to batch his own DIDs' related events. This could be useful for a case like a car manufacturer that would like to batch all DIDs
      associated to their cars, allowing car owners to de-register from a batcher at will.
\item a priori, we do not see a need to batch credential issuance/revocation events
\end{itemize}
\end{document}

>>>>

\newcommand{\todo}[1]{{\colorbox{red}{\bf TODO:}\textcolor{red}{#1}}}

@@

\subsection{Specific Sub-Protocols}
\label{ssec:subproto}

\subsubsection{End-to-End Encrypted Data Exchange via the Connector}
\label{sssec:e2eeconnector}

Assuming each participant of the system owns a (set of) DIDs, we want to let
holders receive new credentials from issuers, in a secure -- yet convenient --
manner. We describe a protocol for this purpose.  At the moment, we require
that issuer and prospective holder can perform a one-time physical interaction
with each other or, alternatively, that they have a secure channel at their
avail (although possibly cumbersome to use, hence we only require to use it
once).

In a nutshell, the proposed protocol is composed essentially of two phases. In
the first phase, the issuer shares a QR code with the holder. This QR code
contains the issuer's public key (or, maybe, its DID), a random value, and a
session identifier. This exchange takes place through a secure (i.e.,
confidential and authenticated) channel, such as physical exchange. Probably
immediately, although also possibly at a later point in time, the prospective
holder sends back her own public key (or, alternatively, her DID) and the
session identifier, all authenticated with a MAC, where we use the random value
in the QR code as secret key. The issuer uses the session identifier to locate
the corresponding session and, now that it received in an authenticated manner
the public key of the holder, can leverage hybrid encryption techniques to
establish an end-to-end encrypted session, e.g., using ECIES \cite{abr01}.
Ensuring end-to-end encryption and authentication is important at this point, as
all the information exchanged between issuer and holder is routed through the
connector: an entity or set of entities who ensure that asynchronous
communication can take place between issuer and holder. Thus, ECIES is crucial
to ensure the secrecy and authenticity of the information, end-to-end.

We have modelled this protocol using Tamarin%
\footnote{https://tamarin-prover.github.io/ (Last access, October 5th, 2021.)}

@@

Notes:
\begin{itemize}
\item we could change the $CreateDID$ event to incorporate an optional batcher DID from start, the batcher DID would be part of the initial state, 
      bounding the batcher to the DID suffix. 
\item we could support events to de-register from a batcher, and to switch batcher too.
\item a user is free to batch his own DIDs' related events. This could be useful for a case like a car manufacturer that would like to batch all DIDs
      associated to their cars, allowing car owners to de-register from a batcher at will.
\item a priori, we do not see a need to batch credential issuance/revocation events
\end{itemize}

\bibliographystyle{plain}
\bibliography{article}

\end{document}
